Article Title

### 2013-08-08 sections/Theory.tex
updated the Theory section.

\subsection{Theory and notation}

\paragraph{Problem setup:}

@@

The observations need not be independently and identically sampled from $F$. The only assumption is that the data generating process is ergodic, \emph{i.e.}\;that $\max_x \left[\hat F_n(x) - F(x)\right] \to 0$ as the sample size $n$ increases. Then each $x_i$ can be thought to be drawn from $F$ when not conditioned on nearby observations.

@@

\paragraph{Variance-bias tradeoff:}
Let $\hat\Sigma_\gamma$ be a family of approximate (biased) covariance estimates indexed by $\gamma$. To evaluate each estimate, let's define the \emph{loss function} $\mathcal L : \Theta \times \Theta \mapsto \mathbb R$ such that $\mathcal L(\hat S,S)$ is minimized when $\hat S = S$.  Then \emph{excess loss} $\ell(\hat S, S) = \mathcal L(\hat S, S) - \mathcal L(S,S)$ assumes zero at the minimum. \TODO{This is too abstract -- need to motivate with some examples maybe}

@@

\textbf{Figure 2.}{
Gaussian Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: The Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from pairwise interactions between 
\textbf{D}: A similar covariance matrix with sparse + low-rank inverse with 3 latent units.
}\label{fig:02}

>>>>

\subsection{Overview}
Given a finite sample, the \emph{sample covariance matrix} $\hat\Sigma_0$ is the usual estimator of the \emph{true covariance matrix} $\Sigma$ of the underlying random process.  $\hat\Sigma_0$ is unbiased but, with finite sample sizes, not as close to $\Sigma$ as possible.  More \emph{efficient} estimators can be constructed by \emph{regularization}, which is the deliberate biasing of the usual estmate toward a different, low-dimensional parametric \emph{target estimate} $\hat T$. 
Target estimates are biased approximations because they cannot represent an arbitrary $\Sigma$, but they also have lower random variability.
Regularization reduces the overall error by striking a favorable balance between the variance  (\emph{estimation error}) and the bias \emph{(approximation error)} of the estimate.

Regularization requires making the following three choices: 
\begin{enumerate}[  1. ]
\item define a set of low-dimensional target estimates
\item given the data, select the optimal target estimate from the set 
\item given the data, select the optimal amount of biasing toward the target estimate
\end{enumerate}
The first choice, the selection of the general form of target estimates, must be made \emph{a priori}.  Curiously, \emph{some} improvement can be produced with an arbitrary target estimate as long as its variance is lower than that of the unbiased estimator.  The perplexing fact that estimates can be improved by biasing toward an arbitrary less variable target is known as \emph{Stein's paradox} \citep{Efron:1977}.

\subsection{Probabilistic framework}

@@

The observations need not be independently and identically sampled from $F$. The only assumption is that the data generating process is ergodic, \emph{i.e.}\;that $\max\limits_x \left[\hat F_n(x) - F(x)\right] \to 0$ as the sample size $n$ increases. Then each $x_i$ can be thought to be drawn from $F$ when not conditioned on nearby observations.

@@

\subsection{Measures of error}
Let $\hat\Sigma_\gamma$ be a family of approximate (biased) covariance estimates indexed by $\gamma$. To evaluate each estimate, let's define the \emph{loss function} $\mathcal L : \Theta \times \Theta \mapsto \mathbb R$ such that $\mathcal L(\hat S,S)$ is minimized when $\hat S = S$.  Then \emph{excess loss} $\ell(\hat S, S) = \mathcal L(\hat S, S) - \mathcal L(S,S)$ assumes zero at the minimum. \TODO{This is too abstract -- need to motivate with some examples maybe}

@@

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/Figure2.pdf}
\caption{
%\textbf{Figure 2.}{
Gaussian Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: In the Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from sparse pairwise linear interactions between visible units. 
\textbf{D}: In the Gaussian graphical model with latent units, correlations arise  between pairs of nodes 
}\label{fig:02}
%}
\end{figure}
